Meta-analysis of the Interoceptive Accuracy Scale

### 2025-08-15 analysis/study2.qmd
pool coefficients BPQ- Depression
@DominiqueMakowski I am not sure this is correct

data <- rbind(
  data,
  pool_coef(with = "BPQ_BodyAwareness", component="BPQ", name = "Body Awareness (BPQ)"),
  pool_coef(with = "BPQ_AutonomicReactivity", component="BPQ", name = "Autonomic Reactivity (BPQ)")
  )
```

@@

data <- rbind(
  data,
  #df2 
  make_rez(with = "TAS_DIF", component="Alexithymia", name = "Difficulties Identifying Feelings (TAS)"),
  make_rez(with = "TAS_DDF", component="Alexithymia", name = "Difficulties Describing Feelings (TAS)"),
  make_rez(with = "TAS_EOT", component="Alexithymia", name = "External Thinking (TAS)"),
  make_rez(with = "BVAQ_Affective", component="Alexithymia", name = "Affective (BVAQ)"), 
  make_rez(df2, vars_intero, with = "BVAQ_Cognitive", component="Alexithymia", name = "Cognitive (BVAQ)")
)
```

@@

data <- rbind(
  data,
  make_rez(with = "PHQ2_Sum", component="Mood", name = "Depression (PHQ-2)"),
  make_rez(with = "PHQ15_Sum", component="Mood", name = "Somatic Concerns (PHQ-15)"), 
  make_rez(with = "PHQ9_Sum", component="Mood", name = "Depression (PHQ-9)"), 
  make_rez(with = "BDI_Sum", component="Mood", name = "Depression (BDI)"), 
  make_rez(with = "PHQ4_Depression", component="Mood", name = "Depression (PHQ-2)"),
  make_cor(with = "DEP", component = "Mood", name = "Depression (MFQ)")
)
```

>>>>

data <- rbind(
  data,
  pool_coef(with = "BPQ_BodyAwareness", component="BPQ", name = "Body Awareness (BPQ)",unequalrange=TRUE),
  pool_coef(with = "BPQ_AutonomicReactivity", component="BPQ", name = "Autonomic Reactivity (BPQ)",unequalrange=TRUE)
  )
```

@@

data <- rbind(
  data,
  pool_coef(with = "TAS_DIF", component="Alexithymia", name = "Difficulties Identifying Feelings (TAS)", unequalrange=TRUE),
  pool_coef(with = "TAS_DDF", component="Alexithymia", name = "Difficulties Describing Feelings (TAS)", unequalrange=TRUE),
  pool_coef(with = "TAS_EOT", component="Alexithymia", name = "External Thinking (TAS)",unequalrange=TRUE),
  pool_coef(with = "BVAQ_Affective", component="Alexithymia", name = "Affective (BVAQ)"), 
  pool_coef(with = "BVAQ_Cognitive", component="Alexithymia", name = "Cognitive (BVAQ)")
)
```

@@

data <- rbind(
  data,
  pool_coef(with = "PHQ2_Sum", component="Mood", name = "Depression (PHQ-2)"),
  pool_coef(with = "PHQ15_Sum", component="Mood", name = "Somatic Concerns (PHQ-15)",unequalrange=TRUE), 
  pool_coef(with = "PHQ9_Sum", component="Mood", name = "Depression (PHQ-9)"), 
  pool_coef(with = "BDI_Sum", component="Mood", name = "Depression (BDI)"), 
  pool_coef(with = "PHQ4_Depression", component="Mood", name = "Depression (PHQ-2)"),
  pool_coef(with = "DEP", component = "Mood", name = "Depression (MFQ)")
)
```
